---
title: "3_Analysis"
output: html_document
---

```{r, include = F}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r}
## Startup
rm(list = ls())
library(easypackages)
libraries("tidyverse", "fastDummies", "robumeta", "knitr", "kableExtra")


## Load Data
characteristics <- readRDS("C:\\Users\\isaac\\Google Drive\\Research\\Projects\\Body Dissatisfaction Meta-Analysis\\BD-depression-meta-analysis\\Data\\Clean Data.rds")

df <- readRDS("C:\\Users\\isaac\\Google Drive\\Research\\Projects\\Body Dissatisfaction Meta-Analysis\\BD-depression-meta-analysis\\Data\\Paired Data With Effect Sizes.rds")


## Prepare Follow-up Data
#Reshape to long dataset, code for follow-up time-point, and keep only follow-up outcomes
df.fu <- df %>%
  #Keep only IDs, moderators, outcomes
  select_at(
    #IDs and moderators
    vars(studyID:blindAssign, randUnits:length.days, controlCond, effectLabel, 
         studyCompletion.fu1, studyCompletion.fu2, n.fu1, n.fu2, time.fu1, time.fu2,
    #Outcomes
    matches("^g.fu[1-2].*$"), matches("^varG.fu[1-2].*$"))) %>%
  #Pivot from wide (two follow ups in each row) to long (each row is one follow up and thus one effect size)
  pivot_longer(cols = studyCompletion.fu1:varG.fu2_t2,
               names_to = c("var", "followUp"),
               names_sep = "\\.") %>%  
  #Move t2/t1t2 information from followUp variable to var variable
  mutate(var = if_else(var %in% c("studyCompletion", "n", "time"),
                       var,
                       paste0(var, ".fu", gsub(".*(?=_)", "", followUp, perl = T))),
         followUp = gsub("_.*", "", followUp)) %>%
  #Pivot back out wide so we have both t2 and t1t2 variables in each row 
  pivot_wider(names_from = "var",
              values_from = "value") %>%
  #Remove rows with no data
  drop_na(time) %>%
  #Create new labels/moderators
  mutate(groupByMeasure = effectLabel,
         effectLabel = paste0(effectLabel, " (", time, " weeks)"),
         followUpLength = case_when(time < 3 ~ "Less than 3 weeks",
                                    time <= 12 ~ "Between 3 and 12 weeks",
                                    time > 12 ~ "Greater than 12 weeks"))
```

# Characteristics of included studies

```{r}
characteristics %>%
  filter(!duplicated(article)) %>%
  select(year:blindAssign, studyCompletion.post:studyCompletion.fu2) %>%
  dummy_cols(remove_selected_columns = T) %>%
  pivot_longer(cols = everything()) %>%
  mutate(name = if_else(name %in% c("studyCompletion.fu1", "studyCompletion.fu2"), "studyCompletion.fu", name)) %>%
  group_by(name) %>%
  summarize(nonmissing = sum(!is.na(value)),
            count = round(sum(value, na.rm = T)),
            min = min(value, na.rm = T),
            max = max(value, na.rm = T),
            mean = mean(value, na.rm = T),
            median = median(value, na.rm = T),
            sd = sd(value, na.rm = T)) %>%
  kable(digits = 2,
        caption = "Study characteristics") %>%
  kable_styling()
```

```{r}
characteristics %>%
  filter(!duplicated(paste0(article, measure))) %>%
  select(measure, respondent, outcome) %>%
  dummy_cols(remove_selected_columns = T) %>%
  pivot_longer(cols = everything()) %>%
  group_by(name) %>%
  summarize(nonmissing = sum(!is.na(value)),
            count = round(sum(value, na.rm = T)),
            min = min(value, na.rm = T),
            max = max(value, na.rm = T),
            mean = mean(value, na.rm = T),
            median = median(value, na.rm = T),
            sd = sd(value, na.rm = T)) %>%
  kable(digits = 2,
        caption = "Measure characteristics") %>%
  kable_styling()
```

```{r}
characteristics %>%
  filter(!duplicated(paste0(article, groupDetailed))) %>%
  select(randUnits.group, pre.n, post.n, fu1.n, fu2.n) %>%
  pivot_longer(cols = everything()) %>%
  group_by(name) %>%
  summarize(nonmissing = sum(!is.na(value)),
            count = round(sum(value, na.rm = T)),
            min = min(value, na.rm = T),
            max = max(value, na.rm = T),
            mean = mean(value, na.rm = T),
            median = median(value, na.rm = T),
            sd = sd(value, na.rm = T)) %>%
  kable(digits = 2,
        caption = "Common group characteristics") %>%
  kable_styling()
```

```{r}
characteristics %>%
  filter(group == "Treatment",
         !duplicated(paste0(article, groupDetailed))) %>%
  select(trtCompletion, interventionParticipant:length.days) %>%
  dummy_cols(remove_selected_columns = T) %>%
  pivot_longer(cols = everything()) %>%
  group_by(name) %>%
  summarize(nonmissing = sum(!is.na(value)),
            count = round(sum(value, na.rm = T)),
            min = min(value, na.rm = T),
            max = max(value, na.rm = T),
            mean = mean(value, na.rm = T),
            median = median(value, na.rm = T),
            sd = sd(value, na.rm = T)) %>%
  kable(digits = 2,
        caption = "Treatment group characteristics") %>%
  kable_styling()
```

```{r}
characteristics %>%
  filter(group == "Control",
         !duplicated(paste0(article, groupDetailed))) %>%
  select(controlCond) %>%
  dummy_cols(remove_selected_columns = T) %>%
  pivot_longer(cols = everything()) %>%
  group_by(name) %>%
  summarize(nonmissing = sum(!is.na(value)),
            count = round(sum(value, na.rm = T)),
            min = min(value, na.rm = T),
            max = max(value, na.rm = T),
            mean = mean(value, na.rm = T),
            median = median(value, na.rm = T),
            sd = sd(value, na.rm = T)) %>%
  kable(digits = 2,
        caption = "Control group characteristics") %>%
  kable_styling()
```

# Meta-analysis

Correlated-effects model with Robust Variance Estimation using `robumeta`

## Post-test effects

### Intercept-only model

#### Using post-test data only

```{r}
model.post.IO_t2 <- robu(formula = g.post_t2 ~ 1,
                         data = df,
                         studynum = studyID,
                         var.eff.size = varG.post_t2,
                         rho = .8,
                         small = T)

print(model.post.IO_t2)

sensitivity(model.post.IO_t2)
```

Depression only

```{r}
df %>%
  filter(outcome == "Depression Symptomatology") %>%
  robu(data = .,
       formula = g.post_t2 ~ 1,
       studynum = studyID,
       var.eff.size = varG.post_t2,
       rho = .8,
       small = T)
```

NA only

```{r}
df %>%
  filter(outcome == "Trait Negative Affect") %>%
  robu(data = .,
       formula = g.post_t2 ~ 1,
       studynum = studyID,
       var.eff.size = varG.post_t2,
       rho = .8,
       small = T)
```

Test of heterogeneity is the I^2 above

#### Using pre- and post-test data

```{r}
model.post.IO_t1t2 <- robu(formula = g.post_t1t2 ~ 1,
                         data = df,
                         studynum = studyID,
                         var.eff.size = varG.post_t1t2,
                         rho = .8,
                         small = T)

print(model.post.IO_t1t2)
```

### Forest plot: 

```{r}
out <- df %>%
  mutate(est = g.post_t2,
         lower = g.post_t2 - (1.96 * sqrt(varG.post_t2)),
         upper = g.post_t2 + (1.96 * sqrt(varG.post_t2)),
         n = n.post,
         article = factor(article)) %>%
  select(article, effectLabel, est, lower, upper, n)

out <- rbind(out,
             tibble(
               article = "Overall Estimate",
               effectLabel = "Overall Estimate",
               est = NA, 
               lower = NA, 
               upper = NA, 
               n = NA
             ))

diamond <- data.frame(x = c(model.post.IO_t2$reg_table["CI.U"][[1]], 
                            model.post.IO_t2$reg_table["b.r"][[1]], 
                            model.post.IO_t2$reg_table["CI.L"][[1]], 
                            model.post.IO_t2$reg_table["b.r"][[1]]), 
                      y = c(1, 1.5, 1, .5),
                      article = "Overall Estimate")

forest.post <- out %>%
  ggplot(aes(y = effectLabel,
             x = est,
             xmin = lower,
             xmax = upper)) +
  geom_point(aes(size = n), 
             shape = "square") +
  geom_errorbarh() +
  scale_y_discrete(name = NULL, 
                   limits = rev) +
  scale_x_continuous(name = "Hedge's g") +
  scale_size_continuous(range = c(1, 4)) +
  facet_grid(article ~ .,
             scales = "free_y",
             space = "free_y",
             switch = "y") +
  theme(strip.placement = "outside",
        strip.text.y.left = element_text(angle = 0),
        legend.position = "none",
        panel.background = element_rect(fill = NA),
        axis.line.x = element_line(size = .5, color = "black"),
        axis.ticks.y.left = element_blank()) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_polygon(data = diamond, 
               aes(x = x, y = y),
               inherit.aes = F,
               fill = "black")

forest.post
ggsave("C:\\Users\\isaac\\Google Drive\\Research\\Projects\\Body Dissatisfaction Meta-Analysis\\IJED Submission\\Figure 2 (Forest Plot, Post-intervention).png",
       width = 175, units = "mm")
```

### Risk of bias assessment

We will assess publication bias with a funnel plot and Egger's test. We do this by regressing each effect's normalized effect estimate (estimate divided by its standard error) against precision (reciprocal of the standard error of the estimate) and testing the significance of the intercept.

```{r}
df <- df %>%
  mutate(seG.post_t2 = sqrt(varG.post_t2),
         gStd.post_t2 = g.post_t2 / seG.post_t2,
         precision.post_t2 = 1 / seG.post_t2)

robu(formula = gStd.post_t2 ~ 1 + precision.post_t2,
     data = df,
     studynum = studyID,
     var.eff.size = varG.post_t2,
     rho = .8,
     small = T)
```

In addition, we tested the following moderators, included in table below: `blindAssign`, `manual`, `preTraining`, `supervision`, `studyCompletion.post`

```{r}
est = model.post.IO_t2$b.r[[1]]
seMax = max(df$seG.post_t2)

#line 1
a1 = c(est, 0)
b1 = c(est + 1.96 * seMax, seMax)
m1 = (b1[2] - a1[2]) / (b1[1] - a1[1])
b1 = -est * m1

#line 2
a2 = c(est, 0)
b2 = c(est - 1.96 * seMax, seMax)
m2 = (b2[2] - a2[2]) / (b2[1] - a2[1])
b2 = -est * m2

funnel.post <- df %>%
  ggplot(aes(g.post_t2, seG.post_t2)) +
  geom_point() +
  scale_x_continuous(name = "Hedge's g", limits = c(est - 1, est + 1)) +
  scale_y_reverse(name = "Standard Error", limits = c(.325, 0), expand = c(0, 0)) +
  geom_vline(xintercept = est) +
  geom_abline(intercept = b1, slope = m1, linetype = 2) +
  geom_abline(intercept = b2, slope = m2, linetype = 2) +
  theme_classic()

funnel.post
ggsave("C:\\Users\\isaac\\Google Drive\\Research\\Projects\\Body Dissatisfaction Meta-Analysis\\IJED Submission\\Figure 4 (Funnel Plot, Post-intervention).png",
       width = 55, height = 55, units = "mm")
```

```{r}
df %>%
  ggplot(aes(g.post_t2, seG.post_t2)) +
  geom_point(aes(color = outcome)) +
  scale_x_continuous(name = "Hedge's g", limits = c(est - 1, est + 1)) +
  scale_y_reverse(name = "Standard Error", limits = c(.325, 0), expand = c(0, 0)) +
  geom_vline(xintercept = est) +
  geom_abline(intercept = b1, slope = m1, linetype = 2) +
  geom_abline(intercept = b2, slope = m2, linetype = 2) +
  theme_classic()
```

```{r}
df %>%
  ggplot(aes(g.post_t2, n.pre)) +
  geom_point() +
  scale_x_continuous(name = "Hedge's g", limits = c(est - 1, est + 1)) +
  scale_y_continuous(name = "n") +
  geom_vline(xintercept = est) +
  theme_classic()
```

### Moderation tests

Moderation tests for each of the following variables (pre-registered), including subgroups with n >= 3 studies (not effect sizes).

See for minimum n/group in moderator test (they suggest 4, we use 3): Fu, R., Gartlehner, G., Grant, M., Shamliyan, T., Sedrakyan, A., Wilt, T. J., ... & Trikalinos, T. A. (2011). Conducting quantitative synthesis when comparing medical interventions: AHRQ and the Effective Health Care Program. Journal of clinical epidemiology, 64(11), 1187-1197. <https://www.researchgate.net/post/Does-anyone-have-any-citations-supporting-a-specific-number-of-studies-eg-3-or-more-per-subgroup-in-a-categorical-moderator-analysis>

Pre-registered moderators: `year`, `pubStatus`, `country`, `sampleSource`, `meanAge`, `pctFemale`, `pctNonwhite`, `interventionType`, `riskScreen`, `outcome`, `controlCond`, `deliveryFormat`, `target`, `provider`, `supervision`, `length.minutes`, `length.sessions`, `length.days`, `trtCompletion`, `studyCompletion.post`

Added after pre-registration: `interventionParticipant`, `randUnits`

Moderators tested for quality assessment: `blindAssign`, `manual`, `preTraining`, `supervision`, `studyCompletion.post`

Dropped due to zero variation:

- `pctSexualMinority`: All `NA`
- `respondent`: All "Youth-reported"
- `manual`: All "Treatment manual used" or `NA`
- `preTraining`: All "Present" or `NA`

Dropped because only one category had >= 3 studies:

- `pubStatus`: Only 1 not "Peer-reviewed"
- `sampleSource`: Only 1 not "Community sample"
- `controlCond`: Only 2 "Psychoeducation," 1 "Other"
- `delieryFormat`: Only 1 not "Group" 
- `provider`: Only 1 "Self-administered," 1 "Other"
- `interventionParticipant`: Only 2 not "Youth"
- `blindAssign`: Only 1 not "No blind assignment"

Dropped because couldn't establish IRR: 

- `target`

```{r}
moderators <- c(
  #Study characteristics
  "year", "country", 
  #Sampling
  "interventionType", "riskScreen", 
  #Population
  "meanAge", "pctFemale", "pctNonwhite", 
  #Intervention
  "length.minutes", "length.sessions", "length.days", "trtCompletion",
  #Outcome
  "outcome",
  #Quality assessment
  "supervision", "studyCompletion.post", "randUnits")

out <- tibble(
  moderator = NA_character_,
  level = NA_character_,
  nStudies = NA_real_,
  nES = NA_real_,
  subgroupEst = NA_real_,
  subgroupP = NA_real_,
  coef = NA_real_,
  overallStat = NA_real_,
  overallP = NA_real_
)

for(moderator in moderators) {
  
  class <- class(df[[moderator]])
  
  if(class == "numeric") {
    
    model <- robu(formula = as.formula(paste0("g.post_t2 ~ 1 + ", moderator)),
                  data = df[!is.na(df[[moderator]]),],
                  studynum = studyID,
                  var.eff.size = varG.post_t2,
                  rho = .8,
                  small = T)
    
    coef = model$reg_table$b.r[2]
    test = "t"
    dfs = round(model$reg_table$dfs[2], 3)
    stat = model$reg_table$t[2]
    p = model$reg_table$prob[2]
    nStudies = length(unique(df$studyID[!is.na(df[[moderator]])]))
    nES = sum(!is.na(df[[moderator]]))
    
    out <- rbind(out, tibble(
      moderator = moderator,
      level = NA,
      nStudies = nStudies,
      nES = nES,
      subgroupEst = NA,
      subgroupP = NA,
      coef = coef,
      overallStat = paste0(test, "(", dfs, ") = ", round(stat, 3)),
      overallP = p
    ))
  
  } else if(class == "character") {
    
    values <- df[[moderator]][!duplicated(df$studyID)]
    table <- table(values)
    levels <- names(table)[table >= 3]
  
    if(length(levels) == 2) {
      
      model <- robu(formula = as.formula(paste0("g.post_t2 ~ 1 + ", moderator)),
                    data = df[df[[moderator]] %in% levels,],
                    studynum = studyID,
                    var.eff.size = varG.post_t2,
                    rho = .8,
                    small = T)
    
      test = "t"
      dfs = round(model$reg_table$dfs[2], 3)
      stat = model$reg_table$t[2]
      p = model$reg_table$prob[2]
      
      out <- rbind(out, tibble(
        moderator = moderator,
        level = NA,
        nStudies = NA,
        nES = NA,
        subgroupEst = NA,
        subgroupP = NA,
        coef = NA,
        overallStat = paste0(test, "(", dfs, ") = ", round(stat, 3)),
        overallP = p
      ))
        
      for(level in levels) {
        
        model <- robu(formula = g.post_t2 ~ 1,
                      data = df[df[[moderator]] %in% level,],
                      studynum = studyID,
                      var.eff.size = varG.post_t2,
                      rho = .8,
                      small = T)
        
        subgroupEst = model$reg_table$b.r
        subgroupP = model$reg_table$prob
        nStudies = length(unique(df$studyID[df[[moderator]] %in% level]))
        nES = sum(df[[moderator]] %in% level)
        
        out <- rbind(out, tibble(
          moderator = moderator,
          level = level,
          nStudies = nStudies,
          nES = nES,
          subgroupEst = subgroupEst,
          subgroupP = subgroupP,
          coef = NA,
          overallStat = NA,
          overallP = NA
        ))
        
      }
      
    } else {
      
      stop(paste0("Character moderator ", moderator, " does not have two levels"))
      
    }
    
  } else {
    
    stop(paste0("Moderator ", moderator, " not numeric or character"))
    
  }
  
}

out <- out[-1,]

out <- out %>%
  mutate(moderator = recode(moderator,
                            "year" = "Year",
                            "country" = "Country", 
                            "interventionType" = "Intervention Type",
                            "riskScreen" = "Risk Screening",
                            "meanAge" = "Mean Age",
                            "pctFemale" = "Percent Female",
                            "pctNonwhite" = "Percent Non-white",
                            "length.minutes" = "Length (Minutes)",
                            "length.sessions" = "Length (Sessions)",
                            "length.days" = "Length (Days)",
                            "trtCompletion" = "Treatment Completion Rate",
                            "outcome" = "Outcome",
                            "supervision" = "Facilitator Supervision",
                            "studyCompletion.post" = "Post-test Data Availability",
                            "randUnits" = "Randomized Units"))

write.csv(out, "C:\\Users\\isaac\\Google Drive\\Research\\Projects\\Body Dissatisfaction Meta-Analysis\\BD-depression-meta-analysis\\Outputs\\Moderator Table - Post-Treatment.csv")

options(knitr.kable.NA = "")
kable(out, digits = 3) %>%
  kable_paper() %>%
  add_header_above(c(" " = 4, "Subgroup Analysis" = 3, "Moderator Test" = 2)) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1, valign = "top")
```

_End of post-test effects analysis._

## Follow-up effects

### Intercept-only model

#### Using follow-up data only

```{r}
model.fu.IO_t2 <- robu(formula = g.fu_t2 ~ 1,
                       data = df.fu,
                       studynum = studyID,
                       var.eff.size = varG.fu_t2,
                       rho = .8,
                       small = T)

print(model.fu.IO_t2)

sensitivity(model.fu.IO_t2)
```

Depression only

```{r}
df.fu %>%
  filter(outcome == "Depression Symptomatology") %>%
  robu(data = .,
       formula = g.fu_t2 ~ 1,
       studynum = studyID,
       var.eff.size = varG.fu_t2,
       rho = .8,
       small = T)
```

NA only

```{r}
df.fu %>%
  filter(outcome == "Trait Negative Affect") %>%
  robu(data = .,
       formula = g.fu_t2 ~ 1,
       studynum = studyID,
       var.eff.size = varG.fu_t2,
       rho = .8,
       small = T)
```

#### Using pre-test and follow-up data

```{r}
model.fu.IO_t1t2 <- robu(formula = g.fu_t1t2 ~ 1,
                         data = df.fu,
                         studynum = studyID,
                         var.eff.size = varG.fu_t1t2,
                         rho = .8,
                         small = T)

print(model.fu.IO_t1t2)
```

### Forest plot

```{r}
out <- df.fu %>%
  mutate(est = g.fu_t2,
         lower = g.fu_t2 - (1.96 * sqrt(varG.fu_t2)),
         upper = g.fu_t2 + (1.96 * sqrt(varG.fu_t2)),
         article = factor(article)) %>%
  select(article, effectLabel, est, lower, upper, n)

out <- rbind(out,
             tibble(
               article = "Overall Estimate",
               effectLabel = "Overall Estimate",
               est = NA, 
               lower = NA, 
               upper = NA, 
               n = NA
             ))

diamond <- data.frame(x = c(model.fu.IO_t2$reg_table["CI.U"][[1]], 
                            model.fu.IO_t2$reg_table["b.r"][[1]], 
                            model.fu.IO_t2$reg_table["CI.L"][[1]], 
                            model.fu.IO_t2$reg_table["b.r"][[1]]), 
                      y = c(1, 1.5, 1, .5),
                      article = "Overall Estimate")

forest.FU <- out %>%
  ggplot(aes(y = effectLabel,
             x = est,
             xmin = lower,
             xmax = upper)) +
  geom_point(aes(size = n), 
             shape = "square") +
  geom_errorbarh() +
  scale_y_discrete(name = NULL, 
                   limits = rev) + 
  scale_x_continuous(name = "Hedge's g") +
  scale_size_continuous(range = c(1, 4)) +
  facet_grid(article ~ .,
             scales = "free_y",
             space = "free_y",
             switch = "y") +
  theme(strip.placement = "outside",
        strip.text.y.left = element_text(angle = 0),
        legend.position = "none",
        panel.background = element_rect(fill = NA),
        axis.line.x = element_line(size = .5, color = "black"),
        axis.ticks.y.left = element_blank()) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_polygon(data = diamond, 
               aes(x = x, y = y),
               inherit.aes = F,
               fill = "black")

forest.FU
ggsave("C:\\Users\\isaac\\Google Drive\\Research\\Projects\\Body Dissatisfaction Meta-Analysis\\IJED Submission\\Figure 3 (Forest Plot, Follow-up).png",
       width = 175, units = "mm")
```

### Risk of bias assessment

```{r}
df.fu <- df.fu %>%
  mutate(seG.fu_t2 = sqrt(varG.fu_t2),
         gStd.fu_t2 = g.fu_t2 / seG.fu_t2,
         precision.fu_t2 = 1 / seG.fu_t2)

robu(formula = gStd.fu_t2 ~ 1 + precision.fu_t2,
     data = df.fu,
     studynum = studyID,
     var.eff.size = varG.fu_t2,
     rho = .8,
     small = T)
```

```{r}
est = model.fu.IO_t2$b[[1]]
seMax = max(df.fu$seG.fu_t2)

#line 1
a1 = c(est, 0)
b1 = c(est + 1.96 * seMax, seMax)
m1 = (b1[2] - a1[2]) / (b1[1] - a1[1])
b1 = -est * m1

#line 2
a2 = c(est, 0)
b2 = c(est - 1.96 * seMax, seMax)
m2 = (b2[2] - a2[2]) / (b2[1] - a2[1])
b2 = -est * m2

funnel.FU <- df.fu %>%
  ggplot(aes(g.fu_t2, seG.fu_t2)) +
  geom_point() +
  scale_x_continuous(name = "Hedge's g", limits = c(est - 1, est + 1)) +
  scale_y_reverse(name = "Standard Error", limits = c(.325, 0), expand = c(0, 0)) +
  geom_vline(xintercept = est) +
  geom_abline(intercept = b1, slope = m1, linetype = 2) +
  geom_abline(intercept = b2, slope = m2, linetype = 2) +
  theme_classic()

funnel.FU
ggsave("C:\\Users\\isaac\\Google Drive\\Research\\Projects\\Body Dissatisfaction Meta-Analysis\\IJED Submission\\Figure 5 (Funnel Plot, Follow-up).png",
       width = 55, height = 55, units = "mm")
```

```{r}
df.fu %>%
  ggplot(aes(g.fu_t2, n)) +
  geom_point() +
  scale_x_continuous(name = "Hedge's g", limits = c(est - 1, est + 1)) +
  scale_y_continuous(name = "n") +
  geom_vline(xintercept = est) +
  theme_classic()
```

### Moderation tests

```{r}
moderators <- c(
  #Study characteristics
  "year", "country", 
  #Sampling
  "interventionType", "riskScreen", 
  #Population
  "meanAge", "pctFemale", "pctNonwhite", 
  #Intervention
  "length.minutes", "length.sessions", "length.days", "trtCompletion",
  #Outcome
  "outcome", "followUpLength",
  #Quality assessment
  "supervision", "studyCompletion", "randUnits")

out <- tibble(
  moderator = NA_character_,
  level = NA_character_,
  nStudies = NA_real_,
  nES = NA_real_,
  subgroupEst = NA_real_,
  subgroupP = NA_real_,
  coef = NA_real_,
  overallStat = NA_real_,
  overallP = NA_real_
)

for(moderator in moderators) {
  
  class <- class(df.fu[[moderator]])
  
  if(class == "numeric") {
    
    model <- robu(formula = as.formula(paste0("g.fu_t2 ~ 1 + ", moderator)),
                  data = df.fu[!is.na(df.fu[[moderator]]),],
                  studynum = studyID,
                  var.eff.size = varG.fu_t2,
                  rho = .8,
                  small = T)
    
    coef = model$reg_table$b.r[2]
    test = "t"
    dfs = round(model$reg_table$dfs[2], 3)
    stat = model$reg_table$t[2]
    p = model$reg_table$prob[2]
    nStudies = length(unique(df.fu$studyID[!is.na(df.fu[[moderator]])]))
    nES = sum(!is.na(df.fu[[moderator]]))
    
    out <- rbind(out, tibble(
      moderator = moderator,
      level = NA,
      nStudies = nStudies,
      nES = nES,
      subgroupEst = NA,
      subgroupP = NA,
      coef = coef,
      overallStat = paste0(test, "(", dfs, ") = ", round(stat, 3)),
      overallP = p
    ))
  
  } else if(class == "character") {
    
    values <- df.fu[[moderator]][!duplicated(df.fu$studyID)]
    table <- table(values)
    levels <- names(table)[table >= 3]
  
    if(length(levels) == 2) {
      
      model <- robu(formula = as.formula(paste0("g.fu_t2 ~ 1 + ", moderator)),
                    data = df.fu[df.fu[[moderator]] %in% levels,],
                    studynum = studyID,
                    var.eff.size = varG.fu_t2,
                    rho = .8,
                    small = T)
    
      test = "t"
      dfs = round(model$reg_table$dfs[2], 3)
      stat = model$reg_table$t[2]
      p = model$reg_table$prob[2]
      
      out <- rbind(out, tibble(
        moderator = moderator,
        level = NA,
        nStudies = NA,
        nES = NA,
        subgroupEst = NA,
        subgroupP = NA,
        coef = NA,
        overallStat = paste0(test, "(", dfs, ") = ", round(stat, 3)),
        overallP = p
      ))
        
      for(level in levels) {
        
        model <- robu(formula = g.fu_t2 ~ 1,
                      data = df.fu[df.fu[[moderator]] %in% level,],
                      studynum = studyID,
                      var.eff.size = varG.fu_t2,
                      rho = .8,
                      small = T)

        nStudies = length(unique(df.fu$studyID[df.fu[[moderator]] %in% level]))
        nES = sum(df.fu[[moderator]] %in% level)
        subgroupEst = model$reg_table$b.r
        subgroupP = model$reg_table$prob
          
        out <- rbind(out, tibble(
          moderator = moderator,
          level = level,
          nStudies = nStudies,
          nES = nES,
          subgroupEst = subgroupEst,
          subgroupP = subgroupP,
          coef = NA,
          overallStat = NA,
          overallP = NA
        ))
        
      }
      
    } else {
      
      stop(paste0("Character moderator ", moderator, " does not have two levels"))
      
    }
    
  } else {
    
    stop(paste0("Moderator ", moderator, " not numeric or character"))
    
  }
  
}

out <- out[-1,]

out <- out %>%
  mutate(moderator = recode(moderator,
                            "year" = "Year",
                            "country" = "Country", 
                            "interventionType" = "Intervention Type",
                            "riskScreen" = "Risk Screening",
                            "meanAge" = "Mean Age",
                            "pctFemale" = "Percent Female",
                            "pctNonwhite" = "Percent Non-white",
                            "length.minutes" = "Length (Minutes)",
                            "length.sessions" = "Length (Sessions)",
                            "length.days" = "Length (Days)",
                            "trtCompletion" = "Treatment Completion Rate",
                            "outcome" = "Outcome",
                            "followUpLength" = "Follow-up Length",
                            "supervision" = "Facilitator Supervision",
                            "studyCompletion" = "Follow-up Data Availability",
                            "randUnits" = "Randomized Units"))

write.csv(out, "C:\\Users\\isaac\\Google Drive\\Research\\Projects\\Body Dissatisfaction Meta-Analysis\\BD-depression-meta-analysis\\Outputs\\Moderator Table - Follow-Up.csv")

options(knitr.kable.NA = "")
kable(out, digits = 3) %>%
  kable_paper() %>%
  add_header_above(c(" " = 4, "Subgroup Analysis" = 3, "Moderator Test" = 2)) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1, valign = "top")
```

_End of follow-up effects analysis._
